---
title: Prediction models for hospitalization external validation study
subtitle: Processing review data
author: "Roemer J. Janse"
date: "2023/03/06"
output:
  word_document:
    toc: yes
    toc_depth: 2
---

# 0. Set-up
```{r, include=FALSE}
# Set knitting options
knitr::opts_chunk$set(echo = FALSE, evaluate = TRUE, tidy = TRUE, cache = FALSE, autodep = TRUE, warning = FALSE, message = FALSE)

# Load packages
pacman::p_load("dplyr",          # Data manipulation
               "tidyr",          # replace_na function & pivot_longer function
               "readxl",         # Reading data from .xlsx
               "writexl",        # Writing data to .xlsx
               "knitr",          # Knitting script
               "tableone",       # Create Table One
               "magrittr"        # Efficient piping
)

```

# 1. Data preparation
```{r} 
# Load data
dat_rev <- read_excel("C:/Users/rjjanse/Onedrive - LUMC/Research/Projects/10. EV_Hosp/data/review_data.xlsx", sheet = "data-extraction", range = "A4:HU21")

# Prepare data
dat_rev <- dat_rev %>%
    # Create indicator for citations (year + name)
    mutate(# Get only last name of first author
           last_name = gsub("\\S* ", "", author),
           # Add year and last name together
           citation = paste(year_publication, last_name),
           # If model developed does not have a name, set to '-'
           mod_nr = ifelse(!is.na(suppressWarnings(as.numeric(mod_nr))), "-", mod_nr),
           # Change mod_nr to factor to make sure stacking models are reported in tables after individual components
           mod_nr = factor(mod_nr, levels = c("-", "1 hospitalization", "6 hospitalizations", "Admission", "Discharge", "CART", "CCI", "Davies", "GBDT", "KNN", "LR", "RF", "SVM",
                                              "Stacking"))) %>%
    # Change CITL and slope from logical to character
    mutate(citl = as.character(citl), slope = as.character(slope)) %>%
    # Sort data on citation and then model name
    arrange(citation, mod_nr)

```

# 2. Table 1. General characteristics
```{r} 
# Create table 1
dat_rev %>%
    # Keep only relevant variables
    dplyr::select(citation, mod_nr, country:cstat) %>%
    # Change missing values to empty
    replace_na(list(citl = "", slope = "", cstat = "")) %>%
    # Change names of columns
    set_colnames(c("Paper", "Model", "Country", "Time period of inclusion", "Design", "Population", "Sample size", "Number of events", "Outcome", "Follow-up time", 
                   "Prediction horizon", "Information goal", "Modelling method", "Number of candidate predictors", "Predictor selection method", "Penalization method",
                   "Validation method", "Calibration-in-the-large", "Calibration slope", "C-statistic")) %>%
    # Kable table
    kable()

```

# 3. Table 2. Baseline characteristics of EQUAL and NECOSAD
```{r}
# Load data for table 2
load("C:/Users/rjjanse/OneDrive - LUMC/Research/Projects/10. EV_Hosp/codes/dataframes/dat_overall.Rdata")

# Create list of variables
var <- c("age", "female", "egfr", "tod", "dm", "ht", "cad", "hf")

# Create list of categorical variables
cat <- c("female", "dm", "ht", "cad", "hf")

# Create table one
dat_overall %>%
    # Create table one
    CreateTableOne(vars = var, factorVars = cat, strata = "src") %>%
    # Print table one
    print(printToggle = FALSE, noSpaces = TRUE, catDigits = 1, contDigits = 1, nonnormal = c("age", "egfr")) %>%
    # Change to matrix
    as.matrix() %>%
    # Keep only relevant columns
    .[, 1:3] %>%
    # Change labels
    set_rownames(c("Number of individuals", "Age, y, median (IQR)", "Women, n (%)", "eGFR, mL/min/1.73m2, median (IQR)", "Time on dialysis, mo, mean (SD)", 
                   "Diabetes mellitus, n (%)", "Hypertension, n (%)", "Coronary artery disease, n (%)", "Heart failure, n (%)")) %>%
    # Change column names
    set_colnames(c("EQUAL", "NECOSAD HD", "NECOSAD PD")) %>%
    # Kable table
    kable()

```

# 4. Table 3. Risk of bias according to PROBAST (concise)
```{r}
# Create base of table 2
tab_2 <- dat_rev %>%
    # Keep only relevant variables
    dplyr::select(citation, mod_nr, d1, d2, d3, d4, d1_app, d2_app, d3_app, d4_app, overall_rob, overall_appl)

# Finalize table
cbind(# Citation and model number
      dplyr::select(tab_2, citation, mod_nr),
      # Changed input to low (low risk) and high (high risk)
      do.call("cbind", lapply(colnames(tab_2)[3:length(colnames(tab_2))], \(x){
          # Function for changing input
          dat_rev %>%
              # Keep only column of iteration
              dplyr::select(all_of(x)) %>%
              # Change variable name
              rename(input = 1) %>%
              # Change input
              mutate(input = case_when(input == "Low risk of bias" ~ "Low",
                                       input == "Low concern" ~ "Low",
                                       input == "High risk of bias" ~ "High",
                                       input == "High concern" ~ "High",
                                       input == "Not reported" ~ "?"))}))) %>%
    # Change names of table 
    set_colnames(c("Paper", "Model", "Participants", "Predictors", "Outcome", "Analysis", "Participants", "Predictors", "Outcome", "Analysis", "ROB", "Applicability")) %>%
    # Kable table
    kable()

```

# 5. Supplementary table 1. Population characteristics of each model and the external validation datasets
```{r}
# Create supplementary table 1
dat_rev %>%
    # Keep only relevant variables
    dplyr::select(citation, mod_nr, age, women, egfr, dial_dur, prev_hosp, dm, hyp, cad, hf) %>%
    # Set missing variables to empty
    replace_na(list(age = "", women = "", egfr = "", dial_dur = "", prev_hosp = "", dm = "", hyp = "", cad = "", hf = "")) %>%
    # Change 1.0 HF to 100% HF
    mutate(hf = ifelse(hf == "1.0", "100%", hf)) %>%
    # Change column names
    set_colnames(c("Paper", "Model", "Age", "Women", "eGFR", "Dialysis duration", "Previous hospitalizations", "Diabetes mellitus", "Hypertension", 
                   "Coronary artery disease", "Heart failure")) %>%
    # Write to .xlsx (kable() does not work due to cell content)
    write_xlsx(., path = "C:/Users/rjjanse/OneDrive - LUMC/Research/Projects/10. EV_Hosp/codes/results/st1.xlsx")

```

# 6. Supplementary table 2. Detailed characteristics of each included model
```{r}
# Create supplementary table 2
dat_rev %>%
    # Keep only relevant variables
    dplyr::select(citation, mod_nr, pop_crit:limitations) %>%
    # Replace missings
    replace_na(list(`brier score` = "", eci = "", sensitivity = "", Specificity = "", gm = "", `hl-test` = "")) %>%
    # Change column names
    set_colnames(c("Paper", "Model", "Eligibility criteria", "Recruitment method", "Definition", "Measurement", "Consistent", "Type", "Blinded assessment", "Incorporation bias",
                   "EPV", "% Missing", "Missing data handling", "Assumptions satisfied", "Candidate predictor selection", "AIC", "Brier score", "ECI", "Sensitivity", 
                   "Specificity", "GM", "Hosmer-Lemeshow test", "Alternative presentation", "Compared development and validation dataset", "Interpretation", 
                   "Comparison with other studies", "Generalizability", "Strengths", "Limitations")) %>%
    # Write to .xlsx (kable() does not work due to cell content)
    write_xlsx(., path = "C:/Users/rjjanse/OneDrive - LUMC/Research/Projects/10. EV_Hosp/codes/results/st2.xlsx")

```

# 7. Supplementary table 3. Characteristics of candidate predictors
```{r}
# Create supplementary table 3
dat_rev %>%
    # Keep only relevant variables
    dplyr::select(citation, mod_nr, pred_1:hand_23) %>%
    # Complete pivot longer
    pivot_longer(pred_1:hand_23, names_to = c("var", "nr"), names_pattern = "(\\w+)_(\\d+)", values_to = "val") %>%
    # Pivot wider on var names
    pivot_wider(id_cols = c(citation, mod_nr, nr), names_from = var, values_from = val, names_repair = "check_unique") %>%
    # Remove NAs
    filter(!is.na(pred)) %>%
    # Remove number column
    dplyr::select(-nr) %>%
    # Change column names
    set_colnames(c("Paper", "Model", "Predictor", "Type", "Definition", "Measurement", "Blinded assessment", "Handling in model")) %>%
    # Kable table
    kable()

```

# 8. Supplementary table 5. Risk of bias according to PROBAST (complete)
```{r}
# Create supplementary table 5
tab_s5 <- dat_rev %>%
    # Keep only relevant variables
    dplyr::select(citation, mod_nr, s11:overall_appl)
    
# Finalize table
cbind(# Citation and model number
      dplyr::select(tab_s5, citation, mod_nr),
      # Changed input to low, high, ?, Y, N, PY, and PN
      do.call("cbind", lapply(colnames(tab_s5)[3:length(colnames(tab_s5))], \(x){
          # Function for changing input
          dat_rev %>%
              # Keep only column of iteration
              dplyr::select(all_of(x)) %>%
              # Change variable name
              rename(input = 1) %>%
              # Change input
              mutate(input = case_when(input == "Low risk of bias" ~ "Low",
                                       input == "Low concern" ~ "Low",
                                       input == "High risk of bias" ~ "High",
                                       input == "High concern" ~ "High",
                                       input == "Not reported" ~ "?",
                                       input == "Yes" ~ "Y",
                                       input == "No" ~ "N",
                                       input == "Probably yes" ~ "PY",
                                       input == "Probably no" ~ "PN"),
                     input = ifelse(is.na(input), "NR", input))
      }))) %>%
    # Change column names
    set_colnames(c("Paper", "Model", "Appropriate data", "Appropriate eligibility", "Overall", "Applicability", "Consistent definition and assessment", "Blinded assessment", 
                   "Available at intended model use", "Overall", "Applicability", "Appropriate definition", "Prespecified/standard definition", "No predictors in definition", 
                   "Consistent definition and assessment", "Blinded assessment", "Appropriate time interval", "Overall", "Applicability", "Reasonable number of events", 
                   "Appropriate handling of predictors", "All enrolled participants used", "Appropriate missing data handling", "No predictor selection based on univariable analysis", 
                   "Appropriate handling of data complexities", "Appropriate relevant model performance assessment", "Accounting for overfitting and optimism", 
                   "Assigned predictor weights correspond to final multivariable analysis", "Overall", "Applicability", "Risk of bias", "Applicability")) %>%
    # Kable table
    kable()

```